---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsegCerebellum

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegCerebellum/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegCerebellum/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggsegverse.r-universe.dev/badges/ggsegCerebellum)](https://ggsegverse.r-universe.dev/ggsegCerebellum)
<!-- badges: end -->

Cerebellar Atlases for the ggsegverse Ecosystem.

## Installation

```{r, eval = FALSE}
# From r-universe
install.packages("ggsegCerebellum", repos = "https://ggsegverse.r-universe.dev")

# From GitHub
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegCerebellum")
```

## Atlases
### cerebellum_anatom

Anatomical lobules and nuclei (Diedrichsen et al., 2009).

```{r cerebellum_anatom}
library(ggsegCerebellum)
plot(cerebellum_anatom())
```

### cerebellum_buckner7

Buckner 7-network cerebellar parcellation.

```{r cerebellum_buckner7}
plot(cerebellum_buckner7())
```

### cerebellum_buckner17

Buckner 17-network cerebellar parcellation.

```{r cerebellum_buckner17}
plot(cerebellum_buckner17())
```

### cerebellum_ji10

Ji 10-network subcortical parcellation.

```{r cerebellum_ji10}
plot(cerebellum_ji10())
```

### cerebellum_mdtb10

MDTB 10-region task-based parcellation (King et al., 2019).

```{r cerebellum_mdtb10}
plot(cerebellum_mdtb10())
```

### cerebellum_xue10

Xue 10-network individual parcellation.

```{r cerebellum_xue10}
plot(cerebellum_xue10())
```

### cerebellum_nettekoven32

Nettekoven symmetric 32-region hierarchical parcellation.

```{r cerebellum_nettekoven32}
plot(cerebellum_nettekoven32())
```

### cerebellum_nettekoven68

Nettekoven symmetric 68-region hierarchical parcellation.

```{r cerebellum_nettekoven68}
plot(cerebellum_nettekoven68())
```
## Data source

All NIfTI parcellations from [DiedrichsenLab/cerebellar_atlases](https://github.com/DiedrichsenLab/cerebellar_atlases) in MNI space.

- **Date obtained**: 2026-03-28
