---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegCerebellum

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegCerebellum/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegCerebellum/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegCerebellum)](https://ggseg.r-universe.dev/ggsegCerebellum)
<!-- badges: end -->

Cerebellar atlases for the ggseg ecosystem.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegCerebellum")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegCerebellum")
```

## Anatomical atlas

```{r}
#| label: cerebellum-anatom
library(ggseg)
library(ggsegCerebellum)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = cerebellum_anatom(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Buckner 7-network

```{r}
#| label: cerebellum-buckner7
ggplot() +
  geom_brain(
    atlas = cerebellum_buckner7(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Buckner 17-network

```{r}
#| label: cerebellum-buckner17
ggplot() +
  geom_brain(
    atlas = cerebellum_buckner17(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Ji 10

```{r}
#| label: cerebellum-ji10
ggplot() +
  geom_brain(
    atlas = cerebellum_ji10(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## MDTB 10

```{r}
#| label: cerebellum-mdtb10
ggplot() +
  geom_brain(
    atlas = cerebellum_mdtb10(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Xue 10

```{r}
#| label: cerebellum-xue10
ggplot() +
  geom_brain(
    atlas = cerebellum_xue10(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Nettekoven 32

```{r}
#| label: cerebellum-nettekoven32
ggplot() +
  geom_brain(
    atlas = cerebellum_nettekoven32(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Nettekoven 68

```{r}
#| label: cerebellum-nettekoven68
ggplot() +
  geom_brain(
    atlas = cerebellum_nettekoven68(),
    mapping = aes(fill = label),
    show.legend = FALSE
  ) +
  theme_void()
```

## Data source

Diedrichsen J & Zotow E (2015). Surface-based display of volume-averaged
cerebellar imaging data. *PLoS ONE*, 10(7), e0133402.
